\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

\begin{itemize}

    \item{\textbf{Front End:} A front end web app will be created for the demo to provide
    query access to users. They will be able to filter their queries to some extent}
    \item{\textbf{Back End:} The back end will take inputs from the front-end and use it to query
    data from a Microsoft Access database schema which contains all of the metadata related to each
    rat trial session. This metadata will be served for the user and will also be used to connect the
    metadata to the actual trial data objects (Video files, Track files etc...). Whether or not we will
    be able to serve these actual data objects is both time permitting and depends on our FRDR API access ticket
    being sorted out.}
    \item{\textbf{Natural Language Integration: } Our first integration for the project, we will use
    natural language input as a means of filtering the data and providing queries to the back-end. For PoC purposes,
    this will likely just be a ChatGPT wrapper.}

\end{itemize}

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 12\\
Nathan Perry & 12\\
Leo Vugert & 12\\
Jeremy Orr & 12\\
Aidan Goodyer & 12\\
Tim Pokanai & 12\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } [Dr. Henry Szechtman and Dr.Anna Dvorkin-Gheva ]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Nathan Perry & 5\\
Leo Vugert & 5\\
Aidan Goodyer & 5\\
Jeremy Orr & 5\\
Aidan Goodyer & 5\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 13\\
Nathan Perry & 6\\
Leo Vugert & 10\\
Aidan Goodyer & 5\\
Jeremy Orr & 4\\
Tim Pokanai & 7\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } [Tiago de Moraes Machado]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Nathan Perry & 3\\
Jeremy Orr & 2\\
Leo Vugert & 3\\
Tim Pokanai & 3\\
Aidan Goodyer & 3\\
\bottomrule
\end{tabular}
\end{table}

Jeremy missed one meeting due to a mistake regarding what time the meeting was at
(He was literally sitting outside waiting for our meeting to start while we were in it).

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 218 & 100\% \\
Nathan Perry & 81 & 37\% \\
Leo Vugert & 25 & 11.5\% \\
Aidan Goodyer & 38 & 17.4\% \\
Tim Pokanai & 40 & 18.3\% \\
Jeremy Orr & 34 & 15.6\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}

\par{Note that despite what the template says, this table denotes the number
of opened issues (issues created) in the second column and the number of closed issues
in the third column.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Nathan Perry & 70 & 40 \\
Leo Vugert & 1 & 15 \\
Aidan Goodyer & 1 & 23 \\
Jeremy Orr & 52 & 33 \\
Tim Pokanai & 1 & 22 \\
\bottomrule
\end{tabular}
\end{table}

\par{Nathan specifically offered to be in charge of creating issues for each
action item of each new deliverable. Jeremy provided him assistance for the SRS
explaining the big skew in authored issues.}

\section{CICD}

\par{CI/CD will be used via GitHub actions. This includes automated checks that
check our code compiles without errors and passes our created suite of tests. Additionally,
specific project standards will be enforced with these GitHub actions such as sufficient
code reviewers as well as code documentation standards. These checks will all be done as
our development branches get merged into main.}

\section{Team Charter Trigger Items}

\subsection{Trigger Items}
\begin{enumerate}
    \item{Team member misses meeting without providing notice or reason}
    \item{Team member misses meeting without providing an acceptable excuse}
    \item{Team member's contributions do not hold up to the scrutiny of a peer review}
    \item{Team member's contributions do not hold up to the team's final document review}
    \item{Team member's attitude during meetings or discussion is detrimental to the team environment}
    \item{Team member does not contribute their fair share of issues in the Kanban board}
\end{enumerate}

\subsection{Violations}

\par{Refer to above section for corresponding trigger items. The violations will
be summarized anonymously.}
\begin{enumerate}
    \item{1 violation. Meeting with TA}
    \item{0 violations}
    \item{3 violations. Missing parts of sections, corrective feedback given in branch review.}
    \item{1 violation. Team-wide, missing reflection for VnV}
    \item{1 violation. Lack of seriousness in internal meeting, causing unproductive discussions and going over meeting time.}
    \item{3 violations. Contributions to the SRS were fairly uneven, this was resolved through team
    discussion.}
\end{enumerate}

\subsection{Violation Plan}

\par{Refer to above sections for violation and trigger information}

\begin{enumerate}
    \item{No plan needed. Genuine timing mix up, simply be more cautious when identiying meeting details.}
    \item{N/A}
    \item{No plan needed. Branch review requirements are already in place that resolve these issues.}
    \item{Look through deliverable rubric when creating issues (The problem was caused because no reflection issue was made
    in GitHub). This will ensure that all supplementary parts are accounted for, not just the main document.}
    \item{Communicate with team members about meeting expectations. Meetings should be taken seriously,
    otherwise we are just wasting each other's time.}
    \item{A plan for issue creation and division of labour before starting each deliverable has been implemented.
    This provides a framework for what is expected from everyone and still allows for things to be switched up later if need be.
    This issue has been resolved and is no longer a concern.}
\end{enumerate}

\section{Additional Productivity Metrics}

\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.}

\end{document}