% THIS DOCUMENT IS FOLLOWS THE VOLERE TEMPLATE BY Suzanne Robertson and James Robertson
% ONLY THE SECTION HEADINGS ARE PROVIDED
%
% Initial draft from https://github.com/Dieblich/volere
%
% Risks are removed because they are covered by the Hazard Analysis
\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,      % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\newcommand{\lips}{\textit{Insert your content here.}}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software} 
\author{\authname}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\textbf{Date}} & {\textbf{Version}} & {\textbf{Notes}}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\\

~\newpage
\section{Purpose of the Project}
\subsection{User Business}

\par{The business of the user is to use the system to aid in the
creation and analysis of experiments relating to a large but fragmented data set
of rat trials that investigate compulsive behaviour of rats and how they relate to various 
factors such as drug injections or brain legions. This data set is comprised of videos of rats
moving on a flat surface, files of their (x,y) coordinates and plots that show the trajectories
of these coordinates. Users may want to
extract a concise set of pre-existing data that can be applicable to
their hypothesis to streamline their workflow and avoid the necessity of carrying out trials.
Users may also want to use the system to provide analysis on the data set as a means of
further supplementing ther academic work. This can include drawing behavioural metrics of the rats
based on various parameters (i.e. rate of compulsion based on injection type) or data visualizations
based similarily on compulsive behaviours as they relate to attributes of the rats.}

\lips
\subsection{Goals of the Project}

\par{The high-level goal of the project is to provide users in the field of behavioural sciences,
a unified and non-technical way of drawing from the vast amount of available data on OCD rat trials
to aid in their academic work and experiments. This will be accomplished via the following sub-goals:}

\begin{itemize}
    \item Create a DBMS that provides query access to the entirety of the data set of rat trials as well as all metadata associated with the data.
    \item Provide a UI that makes querying this data approachable to non-technical users by incorporating familiar and intuitive filtering and searching techniques
    (Attribute filters, Natural Language search bar). Further the UI must provide users with pre-generated query options that are likely to
    be useful for users that may not know where to start. This could include selecting all rat trials of a particular drug injection along with
    all saline control data.
    \item Provide an algorithm that can identify compulsive behaviour by looking at each rat trial
    and provide options for behavioural metrics and data visualizations based on various attributes that the user can extract 
    for their purposes.
\end{itemize}


\lips
\section{Stakeholders}
\subsection{Client}

\par{The clients for this project are Dr. Henry Szechtman and Dr. Anna Dvorkin-Gheva, two professors at McMaster University who are experts in
the fields of Psychiatry and Behavioural Neurosciences and Bioinformatics, respectively. They have worked extensively with these OCD rat trials and
were responsible for generating and depositing this data in the FRDR repository where it currently is stored. Dr. Szechtman and Dr. Dvorkin-Gheva want
to drastically improve the availability of the vast data set they have created so that the trials they conducted can become useful to other students and academics in related fields.}
\lips
\subsection{Customer}

\par{Since our application is intended to be open-source and accessible to the public for free, our customers will simply be a group of end-users
of our application. Our end users will primarily involve behavioural neuroscience researchers like Dr. Henry Szechtman and Dr. Anna Dvorkin-Gheva, 
as well as graduate students and lab members, who will all benefit from the user-friendly and accessible functionality of the platform. 
Additionally we will have data scientists as customers, who will benefit from our application architecture anf offered functionality for 
their purposes. Lastly, collaborating institutions and organizations from the open research community will be users of our application, 
since the application is intended to be free-use and accessible to all.}
\lips
\subsection{Other Stakeholders}
\lips
\subsection{Hands-On Users of the Project}
\lips
\subsection{Personas}
\lips
\subsection{Priorities Assigned to Users}
\lips
\subsection{User Participation}
\lips
\subsection{Maintenance Users and Service Technicians}
\lips

\section{Mandated Constraints}
\subsection{Solution Constraints}
\lips
\subsection{Implementation Environment of the Current System}
\lips
\subsection{Partner or Collaborative Applications}
\lips

\begin{tabular}{|m{5cm}|m{10cm}|}
    \hline
    Collaborative System & System Overview \\
    \hline
    FRDR Repository & The Federated Research Data Repository is a 'bilingual bilingual publishing 
    platform for sharing and 
    preserving Canadian research data. 
    It is a curated, general-purpose repository, 
    custom built for large datasets.' This is where the data set of the rat trials is physically located
    and is dispersed across 29 independent datasets. Our system will provide a unified database schema but will
    pull data from this repository.\\
    \hline
    ratbat.mcmaster.ca & While not a directly collaborative system, this is a system made by a previous years' capstone
    team to address the same problem that our system seeks to. It will be a collaborative system in the sense that ir provides
    a reference of potential ways to approach our solution, ideas that work well and can be carried forward
    and providing visibility to shortcomings of the system will help us to avoid repeating mistakes. \\
    \hline
\end{tabular}

\subsection{Off-the-Shelf Software}

\begin{itemize}
    \item The system shall make use of the FRDR API in order to fetch the relevant data from the data set as we will not be hosting a seperate database to physically store the data for our system
    \item In the case of implementing natural language processing, an Off-the-Shelf LLM will be used to accomplish this (In other words we will not be writing our own LLM model for this purpose).
    Note that this model may need to be trained to provide results that are acceptable for our purposes.
\end{itemize}

\subsection{Anticipated Workplace Environment}
\lips
\subsection{Schedule Constraints}

\par{Due to the nature of the capstone course, the scheduling constraints
map directly to dates in which major deliverable related to the project are due in the capstone course.
They are laid out below:}

\begin{tabular}{|m{5cm}|m{10cm}|}
    \hline
    Project Milestone & Scheduling Constraint\\
    \hline
    Software Requirements Specification & Oct 6 2025\\
    \hline
    Verification and Validation Plan & Oct 27 2025\\
    \hline
    Design Document Revision -1 & Nov 10 2025\\
    \hline
    Proof of Concept Demonstration & Nov 17-28 2025\\
    \hline
    Design Documentation Revision 0 & Jan 19 2025\\
    \hline
    Revision 0 Design Demonstration & Feb 2-13 2025\\
    \hline
    Verification and Validation Report & Mar 9 2025\\
    \hline
    Extras (Performance Report + User Manual) & Mar 9 2025\\
    \hline
    Final System Demonstration & Mar 23-29 2025\\
    \hline
    Final Documentation & April 6 2025\\
    \hline
\end{tabular}




\subsection{Budget Constraints}

\par{There is very limited budget available for this project. The department of Computing and Software at McMaster University 
will provide \$125 CAD for approved expenses. Outside of that funding, we are asked not to exceed spending of \$500 CAD
culmulatively as a team. Thus, the total budget constraints for this project are \$500 CAD in total and \$375 of our team's personal funding.}

\subsection{Enterprise Constraints}
\lips

\section{Naming Conventions and Terminology}
\subsection{Glossary of All Terms, Including Acronyms, Used by Stakeholders
involved in the Project}
\lips

\section{Relevant Facts And Assumptions}
\subsection{Relevant Facts}
\lips
\subsection{Business Rules}
\lips
\subsection{Assumptions}
\lips

\section{The Scope of the Work}
\subsection{The Current Situation}
\lips
\subsection{The Context of the Work}
\lips
\subsection{Work Partitioning}
\lips
\subsection{Specifying a Business Use Case (BUC)}
\lips

\section{Business Data Model and Data Dictionary}
\subsection{Business Data Model}
\lips
\subsection{Data Dictionary}
\lips

\section{The Scope of the Product}

\subsection{Product Boundary}
The product is a web-based data analysis platform designed specifically for the Dr. Szechtman Lab’s OCD behavioral neuroscience dataset. Its scope includes database design, backend services, frontend user interfaces, and data analysis pipelines to enable global researchers to access, search, analyze, and visualize rat behavioral data.

\textbf{In-Scope Features}:
\begin{itemize}
    \item \textbf{Database and Backend}: PostgreSQL schema, FastAPI endpoints, metadata management, video file management.
    \item \textbf{Frontend}: Up to date interface with advanced search/filtering, trajectory visualization, and intuitive design for non-technical researchers.
    \item \textbf{Data Processing}: Python based analysis tools for behavioral metrics, pattern detection algorithms, automated workflows, and an extensible architecture for future video-based analysis.
    \item \textbf{Deployment and Accessibility}: A fully deployed platform accessible to international researchers, with documentation, tutorials, and open-source analysis tools.
\end{itemize}

\textbf{Out-of-Scope Features}:
\begin{itemize}
    \item Direct integration with external datasets outside the OCD rat data repository.
    \item Real-time data collection from new experiments (focus is on analysis of existing dataset).
    \item Advanced machine learning video recognition (future extensibility only, not initial deliverable).
\end{itemize}

This boundary ensures the platform delivers a usable, scalable, and research-ready tool while avoiding scope creep into areas requiring separate infrastructure or regulatory compliance.

\subsection{Product Use Case Table}

\begin{table}[h!]
\centering
\begin{tabular}{|p{2.5cm}|p{2cm}|p{3.0cm}|p{3.0cm}|p{2.5cm}|}
\hline
\textbf{Use Case} & \textbf{Actors} & \textbf{Description} & \textbf{Preconditions} & \textbf{Outcome} \\
\hline
UC1: Search \& Filter Data & Researcher & Query dataset & User logged in; dataset available & Filtered dataset returned \\
\hline
UC2: Download Data & Researcher & Download trials & Dataset query completed & Files downloaded \\
\hline
UC4: Deployment \& Access & DevOps Engineer & Deploy platform online or locally & Backend/frontend configured & Platform accessible \\
\hline
\end{tabular}
\caption{Product Use Case Table}
\end{table}

\subsection{Individual Product Use Cases (PUC’s)}

\begin{description}
\item[PUC1: Search and Filter Data] The researcher searches the dataset using filters such as trial number, injection count, or behavioral pattern. The system returns relevant subsets of data.
\item[PUC2: Download Data] The researcher downloads selected subsets of trials, metadata, or video files for offline analysis.
\item[PUC3: System Deployment and Access] The DevOps engineer deploys the platform to ensure that researchers can access it globally, with necessary backend and frontend services running reliably.
\end{description}

\section{Functional Requirements}
\subsection{Functional Requirements}
\lips

\section{Look and Feel Requirements}



\subsection{Appearance Requirements}

\begin{itemize}
    \item The system shall resemble a webstore or online boutique in which possibly useful queries are packaged and presented for selection to guide 
    a non-technical user audience.
    \item The system shall not overwhelm the user with too many or overly complex visible features as to not intimidate a non-technical user audience.
    \item The system shall present the filtering and searching capabilities of the system in a way that is familiar and intuitive, such as the 
    filtering provided in an online shopping storefront.
\end{itemize}

\subsection{Style Requirements}
\lips

\section{Usability and Humanity Requirements}



\subsection{Ease of Use Requirements}

\begin{itemize}
    \item The system shall have a very low ease of use floor. This floor being scrolling through
    pre-packaged query options and clicking on the one most relevant to their needs.
    \item The system shall have a reasonably low ease of use ceiling with intuitive an intuitive filtering interface
    as well as a simple natural language search interface and provided options for generating metrics and visualizations.
\end{itemize}

\subsection{Personalization and Internationalization Requirements}
\lips



\subsection{Learning Requirements}

\begin{itemize}
    \item Assuming that the user is familiar with nature of the data itself, the system should
    have a learning curve of less than 30 minutes. Users shall easily be able to find and use searching
    mechanisms and querying pre-packaged and custom searches shall be very intuitive.
    \item The system shall provide options to generate available metrics or visualizations based on the queried
    data so the user does not need to learn to create their own.
\end{itemize}

\subsection{Understandability and Politeness Requirements}
\lips
\subsection{Accessibility Requirements}
\lips

\section{Performance Requirements}

\subsection{Speed and Latency Requirements}
\begin{itemize}
    \item The system shall return all query results within 2 seconds for result sets of up to 5,000 records.
    \item All network requests shall have latency below 100 ms under normal operating conditions.
\end{itemize}

\subsection{Safety-Critical Requirements}
\begin{itemize}
    \item There are no safety-critical operations for this system, as it handles only user interface and data processing with no direct impact on human safety.
\end{itemize}

\subsection{Precision or Accuracy Requirements}
\begin{itemize}
    \item All query results shall be accurate and filtered according to user specifications.
    \item There shall be no inconsistencies between the source database and query results.
\end{itemize}

\subsection{Robustness or Fault-Tolerance Requirements}
\begin{itemize}
    \item The system shall log and report all input errors without crashing.
    \item The backend shall handle errors gracefully, storing detailed logs for debugging and monitoring purposes.
\end{itemize}

\subsection{Capacity Requirements}
\begin{itemize}
    \item The system shall support up to 250 concurrent users and handle 5,000 transactions per hour.
    \item The database and associated controllers shall be able to manage up to 11 TB of data.
\end{itemize}

\subsection{Scalability or Extensibility Requirements}
\begin{itemize}
    \item The system shall allow additional modules to be integrated without requiring major changes to existing features.
    \item Under heavy user loads, the system shall maintain at least 80\% of its performance efficiency.
\end{itemize}

\subsection{Longevity Requirements}
\begin{itemize}
    \item The system shall be designed to operate reliably for at least 5 years, with multiple teams and developers able to maintain and extend it.
    \item The system shall be compatible with any operating system when running offline.
\end{itemize}


\section{Operational and Environmental Requirements}
\subsection{Expected Physical Environment}
\begin{itemize}
    \item The system shall be able to run on a standard desktop with atleast 12 GB RAM and average processor.
    \item The software shall function correctly on Windows, macOS, and Linux operating systems.
    \item The software should be able to run in normal office environment conditions which includes temperatures between 15°C and 30°C. 
\end{itemize}

\subsection{Wider Environment Requirements}

\begin{itemize}
    \item The system shall be able to run the top three popular browers.
\end{itemize}


\subsection{Requirements for Interfacing with Adjacent Systems}

\begin{itemize}
    \item Data exchanged with adjacent systems shall use JSON format and be transmitted over HTTPS.
\end{itemize}

\subsection{Productization Requirements}
\begin{itemize}
    \item The system will use Docker and Kubernetes as it's envoirment for assebility to run on all systems.
    \item The system will provide all code changes and software updates on the GitHub Repository. 
\end{itemize}

\subsection{Release Requirements}
\begin{itemize}
    \item The system releases shall follow the versioning defined by MAJOR\#.MINOR\#.PATCH\#.
    \item The system will provide all code changes and software updates on the GitHub Repository. Code then can be pulled and tagged from the appraite GitHub release.
\end{itemize}


\section{Maintainability and Support Requirements}
\subsection{Maintenance Requirements}
\lips
\subsection{Supportability Requirements}
\lips
\subsection{Adaptability Requirements}
\lips

\section{Security Requirements}
\subsection{Access Requirements}

\par{There are no access requirements for our system, since it will be publicly accessible.}

\subsection{Integrity Requirements}

\par{The product shall prevent itself, the databases, and other files within it from intentional abuse.}

\subsection{Privacy Requirements}

\par{The system does not collect or use any user-related data that could be considered private and/or confidential. \newline \indent
The system does not store any personal or sensitive personal data, it only stores and presents the data which is already 
publicly available through FRDR. \newline \indent There are no privacy requirements for the system.}

\subsection{Audit Requirements}

\par{There are no audit requirements for the system. There are no data changes or transactions involved on the user's end 
and they only view already publicly available data, therefore no auditing is required.}

\subsection{Immunity Requirements}
\lips

\section{Cultural Requirements}
\subsection{Cultural Requirements}
\par{There are no cultural requirements for the system.}

\section{Compliance Requirements}
\subsection{Legal Requirements}

\par{There are no legal requirements to be considered for the development of this project. The project does not involve the storage or 
use of user data, it only offers the searching and presentation of an existing public data set. \newline \indent We have consent from our 
supervisors, Dr. Henry Szechtman and Dr. Anna Dvorkin-Gheva to use their data set in the development of the project. Additionally, 
we are allowed to reference the work of the capstone group, ratbat.mcmaster.ca, which they supervised during the previous year.}

\subsection{Standards Compliance Requirements}
\lips

\section{Open Issues}
\lips

\section{Off-the-Shelf Solutions}
\subsection{Ready-Made Products}
\lips
\subsection{Reusable Components}
\lips
\subsection{Products That Can Be Copied}

The client has provided several resources to serve as references for the implementation of the system. These include \href{https://github.com/brandonc-edu/RatBAT/tree/main}{RatBat}: a previous effort to implement an interactive data platform for the OCD rodent dataset, as well as the \href{https://portal.gdc.cancer.gov/analysis_page?app=CohortBuilder&tab=general_diagnosis}{GDC Data Portal} which provides a querying interface that may be replicated by the system. Furthermore, the client expressed a goal of incorporating a user-friendly, e-commerce-like catalogue interface, citing retailers such as \href{https://amazon.ca}{Amazon} as a reference for user interface design. 

\section{New Problems}
\subsection{Effects on the Current Environment}

The new system will be developed from the ground up, there is no current implementation environment to affect. The only existing system that will be interacted with is the FRDR repository which provides
a stable API for accessing the relevant data sets that will be used and will thus be unaffected by any developments made.

\subsection{Effects on the Installed Systems}

\par{ The 'installed system' that concerns this project is the FRDR repository as it will be used as a part of the system to provide the required functionality. The interactions between the new system and
the FRDR repository will all be through a REST API that the FRDR provides. As a result no effects or conflicts are anticipated, although this conclusion operates under the assumption that the provided
API is sound. }


\subsection{Potential User Problems}

\par{An important note to make about the project is that it is not a mandatory replacement for the existing data set and infrastructure 
available through FRDR. Users besides the commissioners of our project, our supervisors, can simply keep using the existing system 
if that better suits their needs. \newline \indent The comissioners of our project, and external users of the project due to its public 
availability, could have a potential issue with the Natural Language Processing (NLP) used in querying raw data files. Since natural language 
will be converted to a query statement using an AI model, it cannot be guaranteed the model will be accurate 100\% of the time when 
creating these queries from natural language.}

\subsection{Limitations in the Anticipated Implementation Environment That May
Inhibit the New Product}
\lips
\subsection{Follow-Up Problems}
\lips

\section{Tasks}
\subsection{Project Planning}
\lips
\subsection{Planning of the Development Phases}
\lips

\section{Migration to the New Product}
\subsection{Requirements for Migration to the New Product}

\par{There are no requirements for migration to the new product other than that the user must familiarize themselves with the new domain and UI if they are used to using the FRDR repository.}


\subsection{Data That Has to be Modified or Translated for the New System}

\par{The new system will take the raw data directly from the FRDR repository and present it to users. There are use cases in which the data will be processed for the purposes 
     of producing metrics or visualizations which is relevant to the functional requirements rather than this section. Thus, no data needs to be modified or translated for this new system.}

\section{Costs}

\par{There are no costs associated with the development of this project.}

\section{User Documentation and Training}
\subsection{User Documentation Requirements}

\begin{itemize}
    \item The system shall be released alongside a user manual guiding users through the possible inputs they have access to, how to properly execute them as well as the corresponding outputs that will be produced as a result. The inputs that 
    will be over: querying pre-packaged result sets, generating custom filters, natural language searching, producing behaviour metrics, producing data visualizations.
\end{itemize}

\subsection{Training Requirements}

\par{ There are no explicit training requirements for this system. The interface should be sufficiently intuitive and the user manual must be interpretable by a non-technical user if they need to learn specific functions.
No explicit training will be needed }

\section{Waiting Room}
\lips

\section{Ideas for Solution}
\lips

\newpage{}
\section*{Appendix --- Reflection}

\input{../Reflection.tex}

\input{../SRS_Reflection.tex}

\end{document}
